### 2023-12-28 doc/Thesis/chapter/01-introduction.tex
digitized all corrections

The remainder of this work is organized with chapter 
%\ref{sec:aims} providing insight into the motivation and the goals. Section \ref{sec:theoretical} gives
\ref{sec:theoretical} giving 
some background information on topics of PV, \td{material science} and \td{computational science} which were used in this work. \td{more detail}
In chapter \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
Section \ref{sec:results} is split into four sections: material specific results are presented in section \ref{sec:res-mat}, results regarding particle swarm optimization in section \ref{sec:res-emma}, further analysis in section \ref{sec:res-post-emma} and discussion of the process and the results in \ref{sec:res-discussion}.
Finally, chapter \ref{sec:outlook} summarizes and discusses the outlook and next steps.

>>>>

The remainder of this work is organized with chapter 
\ref{sec:theoretical} giving 
%some background information on topics of PV, \td{material science} and \td{computational science (more detail)} which were used in this work. 
information on the general \td{functionsweise} of PV, the structure, characteristics and properties of materials which were used and computational, statistical and machine learning methods for data processing.

In chapter \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
Section \ref{sec:results} is split into four sections: material specific results are presented in section \ref{sec:res-mat}, results regarding particle swarm optimization in section \ref{sec:res-emma}, further analysis in section \ref{sec:res-post-emma} and discussion of the process and the results in \ref{sec:res-discussion}.
Finally, chapter \ref{sec:outlook} summarizes and discusses the outlook and next steps.

### 2023-12-28 doc/Thesis/chapter/061-results-emma.tex
digitized all corrections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EMMA}
\label{sec:res-emma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%% ALL SAMPLES
A total of 30 recipes (see appendix \ref{sec:app-emma}) was investigated in 
five iterations ($t = 0, \dots, 4$) of the algorithm. 
Where the first generation encompassed 10 particles and each subsequent generation encompassed 5 particles. 
The \td{best (what is "best"? How do you measure that?	 recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
The experiments for generation 5 where not executed but 
predictions were already made
with the information from the previous generations. 
%%% BEST PREDICTED RECIPE
The sample predicted as best by the algorithm is experiment number 13 with 
lowest $c_{zr}$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$ and second highest $\lambda$. 
%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
%and lowest calcination heating rate and temperature.

@@

%%% OVER TIME 
The only clear trend from table \ref{tab:emma-Gb} is the layer count, which rises with the generations. 
The remaining input variables remained more or less the same except for the 3rd generation. 
%\td{why?}
%
It can be seen in table~\ref{tab:emma-pred-G} 
that the predicted conducticity $\hat{\gamma}$ 
(predicted with 5th generation \gls{rf}; see last column) lowered with each iteration, 
except for sample 2947, which wasn't predicted but measured. 
This shows that the easiest part of the algorithm - the selection of the optimum 
from predicted values - works as expected. 
% and that the predictions included more lower values over time
\begin{table}
	\centering
    \caption{Predicted conductance measure $\hat{\gamma}$ for each generation by each generation's regression function}  
    \label{tab:emma-pred-G}
    \begin{tabular}{cccccc}
        \hline\hline
    enr &1st gen \gls{rf}   &2nd gen \gls{rf} &3rd gen \gls{rf}    &4th gen \gls{rf}   &5th gen \gls{rf}\\
        \hline
    1       &1.214185    &       &       &       &38.7962       \\
    5       &       &4.196626       &       &       &25.47335       \\
    2947    &       &       &10.9594    &       &10.9594       \\
    2405    &       &       &       &20.04962   &25.47335       \\
    13      &       &       &       &       &24.87178   \\
        \hline\hline
    \end{tabular}
\end{table}
%
Contrarily, the predicted conducticity $\hat{\gamma}$ for each generation's best 
(predicted by the very generation's \gls{rf}) does increase with each iteration 
(see diagonal in table~\ref{tab:emma-pred-G}). 
This indicates an underestimation of $\hat\gamma$ at the beginning and a correction with time. 
The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements. 
\linebreak[4]
Indeed, the samples with the lowest \textit{optimizands} are among the initial generation (see figure \ref{fig:emma-G-gen}, figure \ref{fig:emma-phd-gen} and appendix \ref{sec:app-emma}).

%GENERATIONS
In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimizands}, 
conducticity $\gamma$ and pin hole density $\rho$, of each particle at each generation.
The green points at generation number 0 indicate particles which were not included to be propagated. 
%Each violet line indicates a particle, the blue line depicts the average of all particles and the yellow line depicts the average of all particles which were propagated. 
Violet lines connect individual particles in time. 
The blue line connects averages of particles of each generation (including initial non-propagated particles) and 
yellow lines connect averages of each generation of only those particles which were propagated. 
%
Both $\gamma$ and $\rho$ were to be minimized and show a clear trend towards low values with increasing generation, 
indicating that the optimization worked even though 
the prediction functions (see equations~(\ref{eq:emma-phd3})--(\ref{eq:emma-vcal4})) 
and the chosen samples (i.e. chosen input variables) where not exactly as expected. 
Neither expected were the measurements for these samples.
The deviation from expectation might be due to measuring error of samples and variation of quality due to uncontrolled independent variables such as room temperature, humidity or solution age. 
Measurements were expected to show clear correlation of \textit{optimizands} $\gamma$ and $\rho$ with mainly $c_{Zr}$ and $\lambda$.
The only statistically relevant correlation was observed for $T_{cal}$ with the \textit{optimizands}.
%\td{why}
%
In the scatter plots~\ref{fig:g-tcal} and \ref{fig:phd-tcal} the correlation of calcination temperature~$T_{cal}$ with $\gamma$ and $\rho$ can be seen clearly.

@@

The coefficients in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) have the same signs and differ by a factor of roughly 100.
This fits the data well since the maxima of $\rho$ and $\gamma$ are separated by rough factor of 100 (see figure~\ref{fig:emma-gen} and appendix~\ref{sec:app-emma}). %, but the positive influence of the layer count $\lambda$ is counter intuitive 
%as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) 
seem low, but the interaction has -- considering the minimum value of the interaction of $300 \cdot 120 =$  \num{36000} -- several orders of magnitude higher influence on $\rho_3$ and $\gamma_3$ than the $h(6-\lambda)$ term. 
%It's positive the hinge
It is astonishing that the knot of the hinge function for equations (\ref{eq:emma-phd3})--(\ref{eq:emma-vcal3}) was chosen so low; 
basically only including the influence of the lowest layer count $\lambda=4$.
Meaning for equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}), that the lowest layer count produces worse samples which is intuitive, but more than 6 layers don't improve the insulation. 
Encouragingly, the calcination heating rate $v_{cal}$ (see equation (\ref{eq:emma-vcal3})) has been predicted perfectly within numerical precision.

%%% T=4
The coefficients of equations (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) show the same pattern 
as equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}): identical signs and factor 100. 
%The choice of basis functions in combination with their coefficient signs seems more plausible
%for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
%$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $\lambda$ increases the two \textit{optimizands}. 
%
% TCAL ON OPTIMIZANDS
The influence of $T_{cal}$ on the measures of conductance ($\hat\rho$ and $\hat\gamma$) is highly interesting. 
It was expected that 
calcination temperatures under \oc{400} do not suffice to produce compact layers (corresponding to $+h(400-T_{cal})$)
and 
that therefore the resulting layer does not insulate well if $T_{cal}$ is low. 
%This would correspond to $+h(400-T_{cal})$
The original recipe by Hu et al.\cite{Hu2016} used \oc{500} and thus even \oc{400} are low.
\textit{Optimizands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
according to equations~(\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) (see also figures~\ref{fig:g-tcal} and \ref{fig:phd-tcal}), 
ergo the resistance decreases and the conductance increases with increasing calcination temperature contrary to expectations.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{EMMA}
\label{sec:res-emma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%% ALL SAMPLES
A total of 30 recipes (see appendix \ref{sec:app-emma}) was investigated in 
five iterations ($t = 0, \dots, 4$) of the algorithm. 
Where the first generation encompassed 10 particles and each subsequent generation encompassed 5 particles. 
The \td{best (what is "best"? How do you measure that?)} recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
The experiments for generation 5 where not executed but 
predictions were already made
with the information from the previous generations. 
%%% BEST PREDICTED RECIPE
The sample predicted as best by the algorithm is experiment number 13 with 
lowest $c_{zr}$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$ and second highest $\lambda$. 
%lowest solution concentration, second highest layer count, lowest \gls{db} velocity and temperature, 
%and lowest calcination heating rate and temperature.

@@

%%% OVER TIME 
The only clear trend from table \ref{tab:emma-Gb} is the \td{layer count (again not yet clear)}, which rises with \td{the generations (which?)}. 
The remaining input variables remained more or less the same except for the 3rd generation. 
%\td{why?}
%
It can be seen in table~\ref{tab:emma-pred-G} 
that the predicted conducticity $\hat{\gamma}$ 
(predicted with 5th generation \gls{rf}; see last column) lowered with each iteration, 
except for sample 2947, which was not predicted but measured. 
This shows that the easiest part of the algorithm - the selection of the optimum 
from predicted values - works as expected. 
% and that the predictions included more lower values over time
\begin{table}
	\centering
    \caption{Predicted conductance measure $\hat{\gamma}$ for each generation by each generation's regression function}  
    \label{tab:emma-pred-G}
    \begin{tabular}{cccccc}
        \hline\hline
    enr &1st gen \gls{rf}   &2nd gen \gls{rf} &3rd gen \gls{rf}    &4th gen \gls{rf}   &5th gen \gls{rf}\\
        \hline
    1       &1.214185    &       &       &       &38.7962       \\
    5       &       &4.196626       &       &       &25.47335       \\
    2947    &       &       &10.9594    &       &10.9594       \\
    2405    &       &       &       &20.04962   &25.47335       \\
    13      &       &       &       &       &24.87178   \\
        \hline\hline
    \end{tabular}
\end{table}
%
Contrarily, the predicted conducticity $\hat{\gamma}$ for each generation's \td{best (best in what?)}
(predicted by the very generation's \gls{rf}) does increase with each iteration 
(see diagonal in table~\ref{tab:emma-pred-G}). 
This indicates an underestimation of $\hat\gamma$ at the beginning and a correction with time. 
The underestimation probably stems from a lucky selection of initial experiments or a skew in the measurements. 
\linebreak[4]
Indeed, the samples with the lowest \textit{optimizands} are among the initial generation (see figure \ref{fig:emma-G-gen}, figure \ref{fig:emma-phd-gen} and appendix \ref{sec:app-emma}).

%GENERATIONS
\td{How did you determine the pinhole densisty}
In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimizands}, 
conducticity $\gamma$ and pin hole density $\rho$, of each particle at each generation.
The \td{green} points at generation number 0 indicate particles which were not included to be propagated. 
%Each violet line indicates a particle, the blue line depicts the average of all particles and the yellow line depicts the average of all particles which were propagated. 
\td{Violet} lines connect individual particles in time. 
The \td{blue} line connects averages of particles of each generation (including initial non-propagated particles) and 
\td{yellow} lines connect averages of each generation of only those particles which were propagated. 
%
Both $\gamma$ and $\rho$ were to be minimized and show a clear trend towards low values with increasing generation, 
indicating that the optimization worked even though 
the prediction functions (see equations~(\ref{eq:emma-phd3})--(\ref{eq:emma-vcal4})) 
and the chosen samples (i.e. chosen input variables) where not exactly as expected. 
Neither expected were the measurements for these samples.
The deviation from expectation might be due to measuring error of samples and variation of quality due to uncontrolled independent variables such as room temperature, humidity or solution age. 
Measurements were expected to show clear correlation of \textit{optimizands} $\gamma$ and $\rho$ with mainly $c_{Zr}$ and $\lambda$.
The only statistically relevant correlation was observed for $T_{cal}$ with the \textit{optimizands}.
%\td{why}
%
In the scatter plots~\ref{fig:g-tcal} and \ref{fig:phd-tcal} the correlation of calcination temperature~$T_{cal}$ with $\gamma$ and $\rho$ can be seen clearly.

@@

The coefficients in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) have the same signs and differ by a factor of roughly 100.
\td{This (what is "this?)} fits the data well since the maxima of $\rho$ and $\gamma$ are separated by rough factor of 100 (see figure~\ref{fig:emma-gen} and appendix~\ref{sec:app-emma}). %, but the positive influence of the layer count $\lambda$ is counter intuitive 
%as one would expect more layers to be more insulating and thus result in lower conductance and a lower probability of holes going all the way trough the \gls{zro} layers. %pin hole density. 
The coefficients of the $v_{cal} \cdot T_{cal}$ interaction in equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}) 
seem low, but the interaction has -- considering the minimum value of the interaction of $300 \cdot 120 =$  \num{36000} -- several orders of magnitude higher influence on $\rho_3$ and $\gamma_3$ than the $h(6-\lambda)$ term. 
%It's positive the hinge
It is astonishing that the knot of the hinge function for equations (\ref{eq:emma-phd3})--(\ref{eq:emma-vcal3}) was chosen so low; 
basically only including the influence of the lowest layer count $\lambda=4$.
Meaning for equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}), that the lowest layer count produces worse samples which is intuitive, but more than 6 layers do not improve the insulation. 
Encouragingly, the calcination heating rate $v_{cal}$ (see equation (\ref{eq:emma-vcal3})) has been predicted perfectly within numerical precision.

%%% T=4
The coefficients of equations (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) show the same pattern 
as equations (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}): identical signs and factor 100. 
%The choice of basis functions in combination with their coefficient signs seems more plausible
%for (\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) than for (\ref{eq:emma-phd3}) and (\ref{eq:emma-G3}). 
%$\lambda$ decreases $\hat{\gamma}$ and $\hat{\rho}$ and additionally, the lowest $\lambda$ increases the two \textit{optimizands}. 
%
% TCAL ON OPTIMIZANDS
The influence of $T_{cal}$ on the measures of conductance ($\hat\rho$ and $\hat\gamma$) is highly interesting. 
It was expected that 
calcination temperatures under \oc{400} do not suffice to produce compact layers (corresponding to $+h(400-T_{cal})$)
and 
that therefore the resulting layer does not insulate well if $T_{cal}$ is low. 
%This would correspond to $+h(400-T_{cal})$
The \td{original recipe by Hu et al.\cite{Hu2016} used \oc{500} (but to produce Al2O3, so not a surprise? or?)} and thus even \oc{400} are low.
\textit{Optimizands} $\hat\rho$ and $\hat{\gamma}$ increase with higher calcination temperature 
according to equations~(\ref{eq:emma-phd4}) and (\ref{eq:emma-G4}) (see also figures~\ref{fig:g-tcal} and \ref{fig:phd-tcal}), 
ergo the resistance decreases and the conductance increases with increasing calcination temperature contrary to expectations.

### 2023-12-28 doc/Thesis/chapter/07-outlook.tex
digitized all corrections

%\todo{freewriting:} 
%what did i want to do? 
The goal of this work was to find a sol-gel doctor blading process resulting in an insulating zirconium ceramic on top of steel.
This structure then can be used as substrate for thin layer photovoltaics. 
The ceramic needs to be homogeneous and defect free in order to insulate properly.
%what was done? 
A suitable recipe was found\cite{Hu2016} and the process variables were optimized via \gls{emma}. 
The recipe was improved by increasing the stability of the solution. 
The best parameters found by the \gls{emma} optimization were 
$c_{zr}=2$, $\lambda=10$, $v_{DB}=10$, $T_{DB}=40$, $v_{cal}=120$ and $T_{cal}=300$.
%\todo{$T_{cal}=300$}. 
%welche methoden wurden dafür verwendet? 
After optimization, the data was analyzed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
The comparison of methods showed that \gls{emma} performed well on identifying the important correlation between conductance and process variables. 
%was wurde herausgefunden? 
A correlation of calcination temperature and conductance in the range of 300--500\oc{} has been detected.
Furthermore, the layer count has been verified as an important factor. 
%was kann noch herausgefundne werden und wie? 
Next steps include to investigate if the correlation of conductance and calcination temperature are statistically significant or due to small sample size. 
The aging process could be examined via infra red spectroscopy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\iffalse
was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

>>>>

%\todo{freewriting:} 
%what did i want to do? 
The goal of this work was to find a sol-gel doctor blading process resulting in an insulating zirconium ceramic on top of steel.
This structure then can be used as substrate for thin layer photovoltaics. 
The ceramic needs to be homogeneous and defect free in order to insulate properly.
%what was done? 
A suitable recipe was found\cite{Hu2016} and the process variables were optimized via \gls{emma}. 
\td{The recipe was improved by increasing the stability of the solution. (no model needed)}
\td{ALSO: How many exp would you over the computer time and effort to find this out?}
The best parameters found by the \gls{emma} optimization were 
$c_{zr}=2$, $\lambda=10$, $v_{DB}=10$, $T_{DB}=40$, $v_{cal}=120$ and $T_{cal}=300$.
%\todo{$T_{cal}=300$}. 
%welche methoden wurden dafür verwendet? 
After optimization, the data was analyzed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
The comparison of methods showed that \gls{emma} performed well on identifying the important correlation between conductance and process variables. 
%was wurde herausgefunden? 
A correlation of calcination temperature and conductance in the range of 300--500\oc{} has been detected.
Furthermore, the layer count has been verified as an important factor. 
%was kann noch herausgefundne werden und wie? 
Next steps include to investigate if the correlation of conductance and calcination temperature are statistically significant or due to small sample size. 
The aging process could be examined via infra red spectroscopy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\iffalse
was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
